Inferring the Recombinant Genealogy of a Pandemic Pathogen in Real Time

### 2025-09-19 latex/main.tex
Updates from Overleaf

Inspection of the copying patterns for all the recombination events
clearly identified associations between recombination events that failed QC and
known problematic loci in the SARS-CoV-2 genome.
Figure~\ref{fig:copying_pattern_examples} shows illustrative copying patterns
(Q1 to Q4 correspond to the labeled quadrants in Figure~\ref{fig:recombinant_qc}),
in which adjacent sites are underlined in red, and near-adjacent sites (within 3 bases) in orange.
A continuous red+orange underline thus indicates a region treated as a single locus.
Q1 shows a well supported recombination event that passed QC (albeit marginally),
having a net number of supporting loci of 4 on both sides of the breakpoint.
Q2 shows an artefactual recombination event caused by a 9-base Delta lineage-defining deletion.
There are XX (XX\%) of the QC-failing recombination events involving this deletion, and
many cases are affected by a known amplicon dropout caused by this particular deletion \cite{Sanderson2021}
Q3 shows an artefactual recombination event caused by a combination of
this Delta lineage-defining deletion and a known MNS (see below).
Finally, Q4 shows an artifactual recombination event associated with the A507T-T508C-G509A MNS,
which has been identified as a sequencing error due to incomplete read trimming \cite{DeMaio2024}.
There are XX recombination events involving this particular MNS, of which XX\% failed QC.

>>>>

Inspection of the copying patterns for all the recombination events
clearly identified associations between recombination events that failed QC and
known problematic loci in the SARS-CoV-2 genome.
Figure~\ref{fig:copying_pattern_examples} shows illustrative copying patterns
(Q1 to Q4 correspond to the labeled quadrants in Figure~\ref{fig:recombinant_qc}),
in which adjacent sites are underlined in red, and near-adjacent sites (within 3 bases) in orange.
A continuous red+orange underline thus indicates a region treated as a single locus.
Q1 shows a well supported recombination event that passed QC (albeit marginally),
having a net number of supporting loci of 4 on both sides of the breakpoint.
Q2 shows an artefactual recombination event caused by a 9-base Delta lineage-defining deletion.
There are XX (XX\%) of the QC-failing recombination events involving this deletion, and
many cases are affected by a known amplicon dropout caused by this particular deletion \cite{Sanderson2021}
Q3 shows an artefactual recombination event caused by
a combination of this Delta deletion and a known MNS (see below).
Finally, Q4 shows an artifactual recombination event associated with the A507T-T508C-G509A MNS,
which has been identified as a sequencing error due to incomplete read trimming \cite{DeMaio2024}.
There are XX recombination events involving this particular MNS, of which XX\% failed QC.
